### 2020-09-11 paper/perfectGraphs.tex
algoritmicx works with algorithm2e lolz
Contains Pyramid WIP

\paragraph{Finding Pyramids}

\begin{alg}[Test if $G$ contains a Pyramid]
	\label{alg:testPyramid}
	Input: A graph $G$.

	\noindent Output: Returns whether $G$ contains a pyramid as an induced subgraph.
\end{alg}
\begin{algtext}

>>>>

\paragraph{Finding Pyramids}
\begin{alg}[Test if $G$ contains a Pyramid]
	\label{alg:testPyramid}
	Input: A graph $G$.

	\noindent Output: Returns whether $G$ contains a pyramid as an induced subgraph.
\end{alg}
\begin{algorithmic}[1]
	\mProcedure{Contains-Pyramid}{$G$}
	\mForEach{triangle $b_1, b_2, b_3$}
		\mForEach{$s_1, s_2, s_3$, such that for $1 \leq i < j \leq 3$, $\{b_i, s_i\}$ is disjoint
			\lsx  from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them}
			\mIf{there is a vertex $a$, adjacent to all of $s_1, s_2, s_3$, and to at most
				\lsx one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $b_i = s_i$ \lsx}
				\ls $M \gets V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$
				\mForEach{$m \in M$}
					\ls $S_1(m) \gets$ the shortest path between $s_1$ and $m$ such that
					\lsx $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a 
					\lsx path exists.
					\ls calculate $S_2(m), S_3(m)$ similarly
					\ls $T_1(m) \gets$ the shortest path between $m$ and $b_1$, such that
					\lsx $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a
					\lsx path exists
					\ls calculate $T_2(m), T_3(m)$ similarly
				\mEndFor
				\mForEach{$m \in M \cup \{b_1\}$}
					\mIf{$s_1 = b_1$}
						\ls $P_1(b_1) \gets$ the one-vertex path with vertex $b_1$
						\ls \algorithmicforeach ~$m \in M$ \algorithmicdo~ $P_1(m) \gets$ \textsc{undefined}
					\mElse
						\ls $P_1(b_1) \gets $ \textsc{undefined}
						\mForEach{$m \in M$}
							\mIf{ $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$ \AND
								\lsx $S_1(m)$ and $T_1(m)$ both exist \AND
								\lsx $V(S_1(m) \cap T_1(m)) = \{m\}$ \AND
								\lsx there are no edges between $V(S_1(m) \setminus m)$ 
								\lsx and $V(T_1(m) \setminus m)$ 
								\lsx
							}
								\ls $P_1(m) \gets s_1-S_1(m)-m-T_1(m)-b_1$
							\mElse
								\ls $P_1(m) \gets$ \textsc{undefined}
							\mEndIf
						\mEndFor
					\mEndIf
				\mEndFor
				\ls assign $P_2$ and $P_3$ in a similar manner
				\ls $good\_pairs_{1,2} \gets \emptyset$
				\mForEach{$m_1 \in M \cup \{b_1\}$} \Comment{calculate good $(1, 2)$-pairs}
					\mIf{$P_1(m_1) \neq \UND$}
						\ls color black the vertices of $M$ that either belong to
						\lsx $P_1(m_1)$ or have a neighbor in $P_1(m_1)$
						\lsx color all other vertices white.
						\mForEach{$m_2 \in M \cup \{b_2\}$}
							\mIf{$P_2(m_2)$ exists and contains no black vertices}
								\ls add $(m_1, m_2)$ to $good\_pairs_{1,2}$
							\mEndIf
						\mEndFor
					\mEndIf
				\mEndFor
				\ls calculate $good\_pairs_{1,3}$ and $good\_pairs_{2,3}$ in similar way
				\mForEach{triple $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$}
					\mIf{$\forall_{1\leq i < j \leq 3}$: $(m_i, m_j)$ is a good $(i, j)$-pair}
						\ls \RETURN \TRUE
					\mEndIf
				\mEndFor
			\mEndIf
		\mEndFor
	\mEndFor
	\ls \RETURN \FALSE
	\mEndProcedure
\end{algorithmic}

\begin{algtext2}
